Appendix: Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-25 Appendix_plain_AOS.tex
Updates from Overleaf

$\phi$& intercept of the qPCR probability of detection relationship & $\mathcal{N}(3,1)$\\
$\beta0$& intercept of the linear relation between the mean Ct values&$\mathcal{N}(39,3)$\\
&and eDNA concentration (K and E) & \\
$\beta1$& slope of the linear relation between the mean Ct values and &$\mathcal{N}(-1.4,0.05)$\\
&eDNA concentration (K and E) & \\
$\gamma0$& intercept of the linear relation between the standard deviation&$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\gamma1$& intercept of the linear relation between the standard deviation &$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\alpha_s$& species amplification efficiency relative to reference species (R) & fixed (SI Appendix Table S.\ref{tab:alphas})\\
$\zeta$& ethanol wash effect & fixed (-1.15)\\
&&\\
&Index&\\
\hline
$s$& species ($H$ = Hake) & -\\
$j$& location (northing(x), easting(y), depth(d)))& -\\
$i$& biological replicate & -\\
$r$& technical replicate & -\\
$p$& qPCR plate & -\\
$m$& mock community sample & -\\
$q$& qPCR standard aliquote sample & -\\
$R$& metabarcoding reference species & -\\

>>>>

$\phi$& intercept of the qPCR probability of detection relationship & $\mathcal{N}(3,1)$\\
$\beta_0$& intercept of the linear relation between the mean Ct values&$\mathcal{N}(39,3)$\\
&and eDNA concentration (K and E) & \\
$\beta_1$& slope of the linear relation between the mean Ct values and &$\mathcal{N}(-1.4,0.05)$\\
&eDNA concentration (K and E) & \\
$\gamma_0$& intercept of the linear relation between the standard deviation&$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\gamma_1$& intercept of the linear relation between the standard deviation &$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\alpha_s$& species amplification efficiency relative to reference species (R) & fixed (SI Appendix Table S.\ref{tab:alphas})\\
$\zeta$& ethanol wash effect & fixed (-1.15)\\
&&\\
&Index&\\
\hline
$s$& species ($H$ = Hake) & -\\
$j$& location (northing(x), easting(y), depth(d)))& -\\
$i$& biological replicate & -\\
$r$& technical replicate & -\\
$p$& qPCR plate & -\\
$m$& mock community sample & -\\
$q$& qPCR standard aliquote sample & -\\
$R$& metabarcoding reference species & -\\
